### 2018-03-22 morus.tex
MiniMORUS trail

\makeatletter
\pgfdeclareshape{oplus}{%{{{
  \inheritsavedanchors[from=circle]
  \inheritanchorborder[from=circle]
  \foreach \s in {center,mid,base,text, north,south,west,east,
                  mid west,mid east,base west,base east,
                  north west,south west,north east,south east} {
    \inheritanchor[from=circle]{\s}
  }
  \backgroundpath{%
    \pgfutil@tempdima=\radius%
    \pgfmathsetlength{\pgf@xb}{\pgfkeysvalueof{/pgf/outer xsep}}%  
    \pgfmathsetlength{\pgf@yb}{\pgfkeysvalueof{/pgf/outer ysep}}%  
    \ifdim\pgf@xb<\pgf@yb%
      \advance\pgfutil@tempdima by-\pgf@yb%
    \else%
      \advance\pgfutil@tempdima by-\pgf@xb%
    \fi%
    \pgfpathcircle{\centerpoint}{\pgfutil@tempdima}%
    % north-south
    \centerpoint\advance\pgf@y by\radius  \pgf@xa=\pgf@x \pgf@ya=\pgf@y
    \centerpoint\advance\pgf@y by-\radius \pgf@xb=\pgf@x \pgf@yb=\pgf@y
    \pgfpathmoveto{\pgfpoint{\pgf@xa}{\pgf@ya}}
    \pgfpathlineto{\pgfpoint{\pgf@xb}{\pgf@yb}}
    % east-west
    \centerpoint\advance\pgf@x by\radius  \pgf@xa=\pgf@x \pgf@ya=\pgf@y
    \centerpoint\advance\pgf@x by-\radius \pgf@xb=\pgf@x \pgf@yb=\pgf@y
    \pgfpathmoveto{\pgfpoint{\pgf@xa}{\pgf@ya}}
    \pgfpathlineto{\pgfpoint{\pgf@xb}{\pgf@yb}}
  }
}%}}}
\makeatother
\tikzset{op/.style={draw, fill=none, minimum size=1.25ex, inner sep=0pt}}
\tikzset{opxor/.style={op, shape=oplus}}
\tikzset{opand/.style={op, rectangle, rounded corners=2pt, minimum height=3ex}}
\tikzset{oprot/.style={op, rectangle, rounded corners=2pt, inner sep=2pt, minimum width=3ex, font=\scriptsize}}
\tikzset{optee/.style={shape=circle, fill, draw, inner sep=0pt, minimum size=2pt}}
\tikzset{next/.style={->, >=latex}}
\tikzset{trail/.style={line width=2pt, line cap=round}}
\definecolor{delta}{HTML}{B58900}
\definecolor{epsilon}{HTML}{CB4B16}
\definecolor{gamma}{HTML}{6C71C4}
\definecolor{beta}{HTML}{268BD2}
\definecolor{alpha}{HTML}{859900}

@@

\noindent
2 approximations for $S^{2,2}_{0}$:
\begin{align*}
  S^{2,2}_0 &= C^0_{27} \oplus C^1_{0, 8, 26} \oplus C^2_{7,13,31} \oplus C^3_{12} \tag{corr. $2^{-7}$} \\
  S^{2,2}_0 &= C^1_{2} \oplus C^2_{1,7,15,27} \oplus C^3_{6,14,20} \oplus
  C^4_{19} \tag{corr. $2^{-9}$} \\
\intertext{Combined ciphertext-only approximation:}
  0 &= C^0_{27} \oplus C^1_{0, 2, 26, 8} \oplus C^2_{1,13,15,27,31} \oplus
  C^3_{6,12,14,20} \oplus C^4_{19} \tag{corr. $2^{-16}$}
\end{align*}

@@

\begin{figure}
  \substatesfalse
  % \substatesfalse to label state words and/or masks
  \centering
  \begin{subfigure}{.32\textwidth}
  \centering
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail, alpha]
      (C) -- node[right] {$i$} (lll-1)
      (lll-1) -- (tlll-1) (lll-1) -- (xor-1) (xor-1) -- (xnd-1)
      (xnd-1) -- (and-1) (xor-1) -- (txor-1) (txor-1) -- (tanB0) (tanB0) -- (tanB0-|and0.east)
      (and0) -- (xnd0) (xnd0) -- (tlll-1) (xnd0) -- (xor0)
      (and-1.east|-tanA-1) -- (tanA-1) (tanA-1) -- (txor0) (txor0) -- (xor0)
      (xor0) -- (lll0) (lll0) -- (W40) node[below] {$i+b_0$}
      ;
  \end{tikzpicture}%}}}
  \caption*{$\alpha_i$: weight 1} %$C^j_i, S^{j-1,0}_{i+5}$ ($w\!=\!1$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.32\textwidth}
  \centering
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail, beta]
      (C) -- node[right] {$i$} (lll-1)
      (lll-1) -- (tlll-1) (lll-1) -- (xor-1) (xor-1) -- (xnd-1)
      (tlll-1) -- (W-20) node[above] {$i$}
      (xor-1) -- (txor-1) (txor-1) -- (W-21) node[above] {$i$}
      (xnd-1) -- (and-1)
      (W40) node[below] {\phantom{$i$}}
      ;
  \end{tikzpicture}%}}}
  \caption*{$\beta_i$: weight 0} %$C^j_i, S^{j,0}_i, S^{j,1}_i$ ($w\!=\!0$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.32\textwidth}
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail, gamma]
      (W-21) node[above] {$i$} -- (xnd1) (xnd1) -- (xor1) (xor1) -- (lll1)
      (xnd1) -- (and1)
      (xor1) -- (txor1)
      (txor1) -- (W-24) node[above] {$i$}
      (lll1) -- (W41) node[below] {$i+b_1$}
      ;
  \end{tikzpicture}%}}}
  \caption*{$\gamma_i$: weight 1} %$S^{j,1}_i, S^{j,4}_i, S^{j+1,1}_{i-1}$ ($w\!=\!1$)}
  \end{subfigure}
  \bigskip

  \begin{subfigure}{.32\textwidth}
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail, delta]
      (W-24) node[above] {$i$} -- (xnd4) (xnd4) -- (xor4) (xnd4) -- (and4)
      (xor4) -- (lll4) (xor4) -- (txor4) (txor4) -- (W42) node[below] {$i$}
      (lll4) -- (W44) node[below] {$i+b_4$}
      ;
  \end{tikzpicture}%}}}
  \caption*{$\delta_i$: weight 1} %$S^{j,4_i}, S^{j+1,2}_i, S^{j+1,4}_{i+13}$ ($w\!=\!1$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.32\textwidth}
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail, epsilon]
      (W-22) node[above] {$i$} -- (xnd2) (xnd2) -- (xor2) (xnd2) -- (and2)
      (xor2) -- (lll2) (xor2) -- (txor2) (txor2) -- (W40) node[below] {$i$}
      (lll2) -- (W42) node[below] {$i+b_2$}
      ;
  \end{tikzpicture}%}}}
  \caption*{$\varepsilon_i$: weight 1} %$S^{j,2}_i, S^{j+1,0}_i, S^{j+1,2}_{i+7}$ ($w\!=\!1$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.32\textwidth}
    \small
    \begin{align*}
      \intertext{\cipher{MiniMORUS-640}:}
      \alpha_i:      && C_i &\to S^{0}_{i+5} \\
      \beta_i:       && C_i, S^0_i, S^1_i &\to 0 \\
      \gamma_i:      && S^1_i, S^4_i &\to S^1_{i+31} \\
      \delta_i:      && S^4_i &\to S^2_i, S^4_{i+13} \\
      \varepsilon_i: && S^2_i &\to S^0_i, S^2_{i+7}
      \intertext{\cipher{MiniMORUS-1280}:}
      \alpha_i:      && C_i &\to S^{0}_{i+13} \\
      \beta_i:       && C_i, S^0_i, S^1_i &\to 0 \\
      \gamma_i:      && S^1_i, S^4_i &\to S^1_{i+46} \\
      \delta_i:      && S^4_i &\to S^2_i, S^4_{i+4} \\
      \varepsilon_i: && S^2_i &\to S^0_i, S^2_{i+38}
    \end{align*}
    \caption*{\cipher{MiniMORUS} instances}
  \end{subfigure}
  \caption{\cipher{MiniMORUS} linear approximation fragments.}
  \label{fig:minimorus}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}{\textwidth}

    Approximation 1 for $S^{2,2}_0$ (weight 7):

    Step 0: $\alpha_{27}$ (weight 1)

    Step 1: $\alpha_{8,26}, \beta_0, \gamma_0, \delta_0$ (weight 4)

    Step 2: $\alpha_7, \beta_{13,31}, \gamma_{13}$ (weight 2)

    Step 3: $\beta_{12}$ (weight 0)

    Step 4: ---
    \bigskip

    Approximation 2 for $S^{2,2}_0$ (weight 9):

    Step 0: ---

    Step 1: $\alpha_2$ (weight 1)

    St.2: $\alpha_{1,15,27}, \beta_7, \gamma_7, \delta_7, \varepsilon_0$ (weight 6)

    Step 3: $\alpha_{14}, \beta_{6, 20}, \gamma_{20}$ (weight 2)

    Step 4: $\beta_{19}$ (weight 0)
    \caption{\cipher{MiniMORUS-640}}
  \end{subfigure}
  \bigskip

@@

    \caption{\cipher{MiniMORUS-1280}}
  \end{subfigure}
  \caption{\cipher{MiniMORUS} approximations for $S^{2,2}_0$}
\end{figure}

>>>>

\makeatletter
\pgfdeclareshape{oplus}{%{{{
  \inheritsavedanchors[from=circle]
  \inheritanchorborder[from=circle]
  \foreach \s in {center,mid,base,text, north,south,west,east,
                  mid west,mid east,base west,base east,
                  north west,south west,north east,south east} {
    \inheritanchor[from=circle]{\s}
  }
  \backgroundpath{%
    \pgfutil@tempdima=\radius%
    \pgfmathsetlength{\pgf@xb}{\pgfkeysvalueof{/pgf/outer xsep}}%  
    \pgfmathsetlength{\pgf@yb}{\pgfkeysvalueof{/pgf/outer ysep}}%  
    \ifdim\pgf@xb<\pgf@yb%
      \advance\pgfutil@tempdima by-\pgf@yb%
    \else%
      \advance\pgfutil@tempdima by-\pgf@xb%
    \fi%
    \pgfpathcircle{\centerpoint}{\pgfutil@tempdima}%
    % north-south
    \centerpoint\advance\pgf@y by\radius  \pgf@xa=\pgf@x \pgf@ya=\pgf@y
    \centerpoint\advance\pgf@y by-\radius \pgf@xb=\pgf@x \pgf@yb=\pgf@y
    \pgfpathmoveto{\pgfpoint{\pgf@xa}{\pgf@ya}}
    \pgfpathlineto{\pgfpoint{\pgf@xb}{\pgf@yb}}
    % east-west
    \centerpoint\advance\pgf@x by\radius  \pgf@xa=\pgf@x \pgf@ya=\pgf@y
    \centerpoint\advance\pgf@x by-\radius \pgf@xb=\pgf@x \pgf@yb=\pgf@y
    \pgfpathmoveto{\pgfpoint{\pgf@xa}{\pgf@ya}}
    \pgfpathlineto{\pgfpoint{\pgf@xb}{\pgf@yb}}
  }
}%}}}
\makeatother
\tikzset{op/.style={draw, fill=none, minimum size=1.25ex, inner sep=0pt}}
\tikzset{opxor/.style={op, shape=oplus}}
\tikzset{opand/.style={op, rectangle, rounded corners=2pt, minimum height=3ex}}
\tikzset{oprot/.style={op, rectangle, rounded corners=2pt, inner sep=2pt, minimum width=3ex, font=\scriptsize}}
\tikzset{optee/.style={shape=circle, fill, draw, inner sep=0pt, minimum size=2pt}}
\tikzset{next/.style={->, >=latex}}
\tikzset{trail/.style={line width=2pt, line cap=round}}
\definecolor{delta}{HTML}{B58900}
\definecolor{epsil}{HTML}{CB4B16}
\definecolor{gamma}{HTML}{6C71C4}
\definecolor{beta}{HTML}{268BD2}
\definecolor{alpha}{HTML}{859900}

@@

\noindent
2 approximations for $S^{2,2}_{0}$:
\begin{align*}
  S^{2,2}_0 &= C^0_{27} \oplus C^1_{0, 8, 26} \oplus C^2_{7,13,31} \oplus C^3_{12} \tag{corr. $2^{-7}$} \\
  S^{2,2}_0 &= C^1_{2} \oplus C^2_{1,7,15,27} \oplus C^3_{6,14,20} \oplus
  C^4_{19} \tag{corr. $2^{-9}$} \\
\intertext{Combined ciphertext-only approximation:}
  0 &= C^0_{27} \oplus C^1_{0, 2, 26, 8} \oplus C^2_{1,13,15,27,31} \oplus
  C^3_{6,12,14,20} \oplus C^4_{19} \tag{corr. $\approx 2^{-16.5}$}
\end{align*}

@@

\begin{figure}
  \substatesfalse
  % \substatesfalse to label state words and/or masks
  \centering
  \begin{subfigure}{.32\textwidth}
  \centering
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail, alpha]
      (C) -- node[right] {$i$} (lll-1)
      (lll-1) -- (tlll-1) (lll-1) -- (xor-1) (xor-1) -- (xnd-1)
      (xnd-1) -- (and-1) (xor-1) -- (txor-1) (txor-1) -- (tanB0) (tanB0) -- (tanB0-|and0.east)
      (and0) -- (xnd0) (xnd0) -- (tlll-1) (xnd0) -- (xor0)
      (and-1.east|-tanA-1) -- (tanA-1) (tanA-1) -- (txor0) (txor0) -- (xor0)
      (xor0) -- (lll0) (lll0) -- (W40) node[below] {$i+b_0$}
      ;
    \draw[trail, alpha, dashed]
      (and-1.east|-tanB-1) -- (tanB-1) (tanB-1) -- (tanA0) (tanA0) -- (tanA0-|and0.east)
      ;
  \end{tikzpicture}%}}}
  \caption*{$\alpha_i$: weight 1 (not 2)} %$C^j_i, S^{j-1,0}_{i+5}$ ($w\!=\!1$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.32\textwidth}
  \centering
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail, beta]
      (C) -- node[right] {$i$} (lll-1)
      (lll-1) -- (tlll-1) (lll-1) -- (xor-1) (xor-1) -- (xnd-1)
      (tlll-1) -- (W-20) node[above] {$i$}
      (xor-1) -- (txor-1) (txor-1) -- (W-21) node[above] {$i$}
      (xnd-1) -- (and-1)
      (W40) node[below] {\phantom{$i$}}
      ;
  \end{tikzpicture}%}}}
  \caption*{$\beta_i$: weight 1} %$C^j_i, S^{j,0}_i, S^{j,1}_i$ ($w\!=\!0$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.32\textwidth}
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail, gamma]
      (W-21) node[above] {$i$} -- (xnd1) (xnd1) -- (xor1) (xor1) -- (lll1)
      (xnd1) -- (and1)
      (xor1) -- (txor1)
      (txor1) -- (W-24) node[above] {$i$}
      (lll1) -- (W41) node[below] {$i+b_1$}
      ;
  \end{tikzpicture}%}}}
  \caption*{$\gamma_i$: weight 1} %$S^{j,1}_i, S^{j,4}_i, S^{j+1,1}_{i-1}$ ($w\!=\!1$)}
  \end{subfigure}
  \bigskip

  \begin{subfigure}{.32\textwidth}
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail, delta]
      (W-24) node[above] {$i$} -- (xnd4) (xnd4) -- (xor4) (xnd4) -- (and4)
      (xor4) -- (lll4) (xor4) -- (txor4) (txor4) -- (W42) node[below] {$i$}
      (lll4) -- (W44) node[below] {$i+b_4$}
      ;
  \end{tikzpicture}%}}}
  \caption*{$\delta_i$: weight 1} %$S^{j,4_i}, S^{j+1,2}_i, S^{j+1,4}_{i+13}$ ($w\!=\!1$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.32\textwidth}
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail, epsil]
      (W-22) node[above] {$i$} -- (xnd2) (xnd2) -- (xor2) (xnd2) -- (and2)
      (xor2) -- (lll2) (xor2) -- (txor2) (txor2) -- (W40) node[below] {$i$}
      (lll2) -- (W42) node[below] {$i+b_2$}
      ;
  \end{tikzpicture}%}}}
  \caption*{$\varepsilon_i$: weight 1} %$S^{j,2}_i, S^{j+1,0}_i, S^{j+1,2}_{i+7}$ ($w\!=\!1$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.32\textwidth}
    \small
    \begin{align*}
      \intertext{\cipher{MiniMORUS-640}:}
      \alpha_i:      && C_i &\to S^{0}_{i+5} \\
      \beta_i:       && C_i, S^0_i, S^1_i &\to 0 \\
      \gamma_i:      && S^1_i, S^4_i &\to S^1_{i+31} \\
      \delta_i:      && S^4_i &\to S^2_i, S^4_{i+13} \\
      \varepsilon_i: && S^2_i &\to S^0_i, S^2_{i+7}
      \intertext{\cipher{MiniMORUS-1280}:}
      \alpha_i:      && C_i &\to S^{0}_{i+13} \\
      \beta_i:       && C_i, S^0_i, S^1_i &\to 0 \\
      \gamma_i:      && S^1_i, S^4_i &\to S^1_{i+46} \\
      \delta_i:      && S^4_i &\to S^2_i, S^4_{i+4} \\
      \varepsilon_i: && S^2_i &\to S^0_i, S^2_{i+38}
    \end{align*}
    \caption*{\cipher{MiniMORUS} instances}
  \end{subfigure}
  \caption{\cipher{MiniMORUS} linear approximation fragments.}
  \label{fig:minimorus}
\end{figure}

\begin{figure}
  \newcommand{\M}[2]{1.65,-1.5*#1-.25-.25*#2}
  \newcommand{\C}[1]{-.1,-.25-1.5*#1}
  \renewcommand{\S}[2]{.25+.25*#2,-1.5*#1}
  \centering
  \begin{subfigure}{\textwidth}
    \begin{tikzpicture}[xscale=3, yscale=1.5, every node/.style={font=\scriptsize,inner sep=2pt}]
      \foreach \r in {0,...,3} { \draw[gray, rounded corners=2pt] (0,-\r*1.5) rectangle ++(1.5,-1.5); }
      \foreach \r in {0,...,4} { \draw (\S{0}{\r}) node[above] {$S^{\r}$}; }
      \draw (\C{0}|-\S{0}{0}) node[above] {$C$};

      \draw[alpha] (\C{0}) node[left] {27} -| (\S{1}{0}) node[above right] {0}
                   (\M{0}{0}) node[right] {$\alpha_{27}$};

      \draw[beta]  (\C{1}) node[above left] {0} -| (\S{1}{0}) node[below right] {0}
                   (\C{1}-|\S{1}{0}) -| ([xshift=-1pt]\S{1}{1}) node[above] {0\,}
                   (\M{1}{0}) node[right] {$\beta_0$};
      \draw[alpha] ([yshift=-1.5pt]\C{1}) node[left] {8} -| (\S{2}{0}) node[above right] {\!\!13}
                   (\M{1}{1}) node[right] {$\alpha_{8,26}$};
      \draw[alpha] ([yshift=-3.0pt]\C{1}) node[below left] {26} -| ([xshift=-1pt]\S{2}{0}) node[above left] {31\!};
      \draw[gamma] (\S{1}{1}) node[above] {\,0} -- (\S{2}{1}) node[above left] {31\!\!}
                   (\S{1}{1}) ++(0,-.75) -| ([xshift=-1pt]\S{1}{4}) node[above] {0\,}
                   (\M{1}{2}) node[right] {$\gamma_0$};
      \draw[delta] (\S{1}{4}) node[above] {\,0} -- (\S{2}{4}) node[above right] {13}
                   (\S{1}{4}) ++(0,-1.0) -| ([xshift=2pt]\S{2}{2}) node[below] {0} node[black] {$\times$}
                   (\M{1}{3}) node[right] {$\delta_0$};

      \draw[beta]  (\C{2}) node[above left] {31} -| ([xshift=-1pt]\S{2}{0}) node[below left] {31\!}
                   (\C{2}-|[xshift=-1pt]\S{2}{0}) -| ([xshift=0pt]\S{2}{1}) node[below left] {31\!\!}
                   (\M{2}{0}) node[right] {$\beta_{13,31}$};
      \draw[beta]  ([yshift=-1.5pt]\C{2}) node[left] {13} -| (\S{2}{0}) node[below right] {\!\!13}
                   ([yshift=-1.5pt]\C{2}-|\S{2}{0}) -| ([xshift=1pt]\S{2}{1}) node[above] {\,\,\,13};
      \draw[alpha] ([yshift=-3.0pt]\C{2}) node[below left] {7} -| (\S{3}{0}) node[above right] {12}
                   (\M{2}{1}) node[right] {$\alpha_7$};
      \draw[gamma] ([xshift=2pt]\S{2}{1}) node[below right] {13} -- ([xshift=2pt]\S{3}{1}) node[above right] {12}
                   ([xshift=2pt]\S{2}{1}) ++(0,-.75) -| (\S{2}{4}) node[below right] {13}
                   (\M{2}{2}) node[right] {$\gamma_{13}$};

      \draw[beta]  (\C{3}) node[left] {12} -| (\S{3}{0}) node[below right] {12}
                   (\C{3}-|\S{3}{0}) -| ([xshift=2pt]\S{3}{1}) node[below right] {12}
                   (\M{3}{0}) node[right] {$\beta_{12}$};

      \draw (\S{4}{2}) node[above] {\normalsize weight 7};

      \begin{scope}[xshift=2.5cm]
        \foreach \r in {1,...,4} { \draw[gray, rounded corners=2pt] (0,-\r*1.5) rectangle ++(1.5,-1.5); }
        \foreach \r in {0,...,4} { \draw (\S{1}{\r}) node[above] {$S^{\r}$}; }
        \draw (\C{0}|-\S{1}{0}) node[above] {$C$};

        \draw[alpha] (\M{1}{1}) node[right] {$\alpha_2$};

        \draw[beta]  (\M{2}{0}) node[right] {$\beta_7$};
        \draw[alpha] (\M{2}{1}) node[right] {$\alpha_{1,15,27}$};
        \draw[gamma] (\M{2}{2}) node[right] {$\gamma_7$};
        \draw[delta] (\M{2}{3}) node[right] {$\delta_7$};
        \draw[epsil] (\M{2}{4}) node[right] {$\varepsilon_0$};

        \draw[beta]  (\M{3}{0}) node[right] {$\beta_{6,20}$};
        \draw[alpha] (\M{3}{1}) node[right] {$\alpha_{14}$};
        \draw[gamma] (\M{3}{2}) node[right] {$\gamma_{20}$};

        \draw[beta]  (\M{4}{0}) node[right] {$\beta_{19}$};

        \draw (\S{5}{2}) node[above] {\normalsize weight 9};
      \end{scope}
    \end{tikzpicture}
    \caption{\cipher{MiniMORUS-640}}
  \end{subfigure}
  \bigskip

@@

    \caption{\cipher{MiniMORUS-1280}}
  \end{subfigure}
  \caption{\cipher{MiniMORUS}: Two approximations for $S^{2,2}_0$}
\end{figure}
